\section{Evaluation}
\label{sec:goal}
First, evaluated our indirection technique by integer
linear programming (ILP) formulations. In the paper, Liu \textit{et al.\ }~\cite{Liu:2015}
provided a ILP formulation of the scheduling problem without indirection
considerations. We built a new formulation adding indirection to Liu's formulation.
Then used Gurobi~\cite{gurobi}
ILP solver to solve scheduling problems with the two formulations in order
to find the optimal improvement by indirection.

Then we evaluated our indirection techinque in simulation. We received the
simulator of the Solstice algorithm from the authors, and introduced
our techinque into the simulator to compare it with the original algorithm.

%The simulation results will be comparable in terms of number of configurations,
%and the total time to serve all demands.

\section{Conclusion}
\label{sec:conclu}

Recent advances in optical switch technology has created a need for new scheduling
algorithms which take advantage of shorter reconfiguration times while maintaining
reasonable computational overheads. The recent Solstice scheduling algorithm
accomplishes these goals, but does not achieve optimal utilization due to the
fact that it only supports traffic sent over a direct link.
It is possible to meet traffic demands without utilizing a direct link between
each source and destination port by routing traffic over multiple links.
Utilizing these indirect links can reduce the number of reconfigurations necessary
and reduce the amount of unused bandwidth on each link.

In this paper, we have presented an extension to the Solstice packet scheduler allowing for
multi-hop indirect serving of traffic. Through comparison with the original
algorithm in simulation, we have demonstrated that
this indirection technique reduces the number of reconfigurations necessary to serve
all traffic demand by increasing the utilization of each link. 
Our evaluation shows that the indirection technique does not have prohibitively high
computational overhead, and decreases the total amount of time necessary to fulfill
all traffic demands. 
